How reliable are inferences from state-space age-structured assessment models?

### 2023-01-03 Project_0/paper/paper.Rmd

---
title: State-space age-structured assessment models provide reliable inferences(?)
author: 
  - Timothy J. Miller^1^, Britten, Brooks, Fay, Legault, Stock, 
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

But those studies focus primarily on Gaussian 
Reliability of hidden process models

>>>>

---
title: How reliable are inferences from state-space age-structured assessment models?
author: 
  - Timothy J. Miller^1^, Britten, Brooks, Fay, Legault, Stock, 
date: ''
fontsize: 12pt
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    includes:
      in_header:
      - options.sty
      - journalshortcuts.tex
    keep_tex: yes
    number_sections: yes
  html_document:
    df_print: paged
  word_document: default
header-includes:
- \usepackage{xspace}
- \usepackage{bm}
- \usepackage{caption,graphics}
- \usepackage{graphicx}
- \usepackage{makecell}
- \renewcommand\figurename{Fig.}
- \captionsetup{labelsep=period, singlelinecheck=false}
- \newcommand{\changesize}[1]{\fontsize{#1pt}{#1pt}\selectfont}
- \renewcommand{\arraystretch}{1.5}
- \renewcommand\theadfont{}
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
biblio-style: cjfas2.bst
---

@@

But those studies focus primarily on Gaussian linear models.
review literature on reliability of hidden/latent process models. Primarily in other fields.
